IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/real.tex
locking

While the described system implements |specLangJS seqf|, Node.js
applications may require access to the file system, HTTP server, HTTP
client, etc.

>>>>

\Red{LOCK:deian}
While the described system implements |specLangJS seqf|, server-side
applications may require access to the file system, HTTP server, HTTP
client, etc.
%
Unfortunately, our formalism does not capture such external effects
and exposing the Node.js libraries directly to sandboxed tasks is unsafe.
%
Hence, we instead implement libraries such as the file system as
message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
in Figure~\ref{fig:node}) and main Node.js task taht 
%
This is in part because how external effects 
%
Hence, our implementation of l
%This is, in part, because the handling of such effect
